Experiment_2_modelling

### 2020-08-12 Experiment_2/Bayesian_models_exp2.Rmd
added BIC weights and new Bayes model

####### test data 
dat <- subset(dat,human_id == "bZg1T3MNoItL6b7qAAAj")
#######

@@

```{r}
## the following computes probabilities of ai actions assuming
## strategy is always followed.

@@

# if human does not distinguish between players, we can run with these predictions as is
# if human does distinguish between players, we need to set the predictions to uniform at the start of a round

# if human generalizes over games, we can run update the prior generally
# if human generalizes over rounds but not games, we need to reset the prior at the start of a game
# if human does not generalize, we need to reset the prior at the start of each round

Bayes_model_LL <- function(par,data,distinct_opponent = TRUE, generalize = c("game","stage","no")) {
  # data is a subset for a single participant
  generalize <- match.arg(generalize)
  alpha <- par[1] # probability that opponent plays according to strategy
  if(length(par) > 1) {
    beta <- par[2] # probability that human plays according to best response 
  } else{
    beta <- 1 # probability that human plays according to best response 
  }

@@

@@

@@

```{r}
Bayes_model_LL(0.1,data = dat,distinct_opponent = TRUE, generalize = "game")
```

@@

# for(id in levels(dat$human_id)) {
#   tdat <- subset(dat,human_id == id)
#   ctrl <- DEoptim.control(NP = 20, itermax=50)
#   Bayes_same_game[[id]] <- DEoptim(Bayes_model_LL, lower=c(0), upper = c(1), data = tdat,
#                                    distinct_opponent = FALSE, generalize = "game",control=ctrl)
#   Bayes_same_stage[[id]] <- DEoptim(Bayes_model_LL, lower=c(0), upper = c(1), data = tdat,
#                                    distinct_opponent = FALSE, generalize = "stage",control=ctrl)
#   Bayes_same_no[[id]] <- DEoptim(Bayes_model_LL, lower=c(0), upper = c(1), data = tdat,
#                                    distinct_opponent = FALSE, generalize = "no",control=ctrl)
#   Bayes_distinct_game[[id]] <- DEoptim(Bayes_model_LL, lower=c(0), upper = c(1), data = tdat,
#                                    distinct_opponent = TRUE, generalize = "game",control=ctrl)
#   Bayes_distinct_stage[[id]] <- DEoptim(Bayes_model_LL, lower=c(0), upper = c(1), data = tdat,
#                                         distinct_opponent = TRUE, generalize = "stage",control=ctrl)
#   Bayes_distinct_no[[id]] <- DEoptim(Bayes_model_LL, lower=c(0), upper = c(1), data = tdat,
#                                  distinct_opponent = TRUE, generalize = "no",control=ctrl)
# }

@@

for(id in levels(dat$human_id)) {
  tdat <- subset(dat,human_id == id)
  # ctrl <- DEoptim.control(NP = 20, itermax=50)

  Bayes_same_game[[id]] <- optim(c(0.1),fn=Bayes_model_LL,data=tdat, distinct_opponent = FALSE, 
                                 generalize = "game", lower = c(0), upper = c(1),method="L-BFGS-B")

  Bayes_same_stage[[id]] <- optim(c(0.1),fn=Bayes_model_LL,data=tdat, distinct_opponent = FALSE, 
                                 generalize = "stage", lower = c(0), upper = c(1),method="L-BFGS-B")

  Bayes_same_no[[id]] <- optim(c(0.1),fn=Bayes_model_LL,data=tdat, distinct_opponent = FALSE, 
                                 generalize = "no", lower = c(0), upper = c(1),method="L-BFGS-B")

  Bayes_distinct_game[[id]] <- optim(c(0.1),fn=Bayes_model_LL,data=tdat, distinct_opponent = TRUE, 
                                 generalize = "game", lower = c(0), upper = c(1),method="L-BFGS-B")

  Bayes_distinct_stage[[id]] <- optim(c(0.1),fn=Bayes_model_LL,data=tdat, distinct_opponent = TRUE, 
                                 generalize = "stage", lower = c(0), upper = c(1),method="L-BFGS-B")

  Bayes_distinct_no[[id]] <- optim(c(0.1),fn=Bayes_model_LL,data=tdat, distinct_opponent = TRUE, 
                                 generalize = "no", lower = c(0), upper = c(1),method="L-BFGS-B")
}
```

>>>>

####### test data

# dat <- subset(dat,human_id == "bZg1T3MNoItL6b7qAAAj")
# dat <- subset(dat,human_id == "J3SqvTcFUwXtSC6wAAB0")
# dat <- subset(dat,human_id == "gRRZ0rUagyVejWTOAAFl")
dat <- subset(dat,human_id == "vGnDPRowetREQVmwAADL")
# dat <- subset(dat,human_id == "wi_zWhftr9MdqTmCAAHs")

#######

@@

```{r}
## the following computes probabilities of ai actions assuming
## strategy is always followed. (level refers to ai level)

@@

# if human does not distinguish between players, we can run with these predictions as is
# if human does distinguish between players, we need to set the predictions to uniform at the start of a stage

# if human generalizes over games, we can run update the prior generally
# if human generalizes over rounds but not games, we need to reset the prior at the start of a game
# if human does not generalize, we need to reset the prior at the start of each ?stage?

Bayes_model_LL <- function(par,data,distinct_opponent = TRUE, generalize = c("game","stage","no")) {
  # data is a subset for a single participant
  generalize <- match.arg(generalize)
  alpha <- par[1] # probability that ai opponent plays according to strategy
  if(length(par) > 1) {
    beta <- par[2] # probability that human plays according to best response 
  } else{
    beta <- 1 # probability that human plays according to best response 
  }

@@

    # cat(as.character(c(dat$post_level0, dat$post_level1, dat$post_level2)), "\n")

  # use posterior predictive probability to predict probability of each ai and then human action
  # opp is ai and self is human player here
  dat <- dat %>%
    mutate(p_opp_a1 = post_level0*pred_a1_level0 + post_level1*pred_a1_level1 + post_level2*pred_a1_level2,
           p_opp_a2 = post_level0*pred_a2_level0 + post_level1*pred_a2_level1 + post_level2*pred_a2_level2,
           p_opp_a3 = post_level0*pred_a3_level0 + post_level1*pred_a3_level1 + post_level2*pred_a3_level2
    ) %>%
      mutate(p_self_a1 = case_when(
              game == "shootout" ~ (1-beta)*(1/3) + beta*(.5*p_opp_a2 + .5*p_opp_a3),
              TRUE ~ (1-beta)*(1/3) + beta*(p_opp_a3)
                ),
             p_self_a2 = case_when(
               game == "shootout" ~ (1-beta)*(1/3) + beta*(.5*p_opp_a1 + .5*p_opp_a3),
               TRUE ~ (1-beta)*(1/3) + beta*(p_opp_a1)
             ),
             p_self_a3 = case_when(
               game == "shootout" ~ (1-beta)*(1/3) + beta*(.5*p_opp_a1 + .5*p_opp_a2),
               TRUE ~ (1-beta)*(1/3) + beta*(p_opp_a2)
             )
        )

@@

  #cat(as.character(exp(dat$loglik)), "\n", "\n")

@@

```{r}
#Bayes_model_LL(0.5,data = dat,distinct_opponent = TRUE, generalize = "game")

#PLot likelihood for first participant as function of parameter 
likelihoods <- list()
for (t in 1:99) {
  likelihoods[t] <- Bayes_model_LL(t/100,data = dat,distinct_opponent = TRUE, generalize = "game")
}

jpeg(file="vGnDPRowetREQVmwAADL.jpeg")
plot(unlist(likelihoods))
dev.off()

@@

for(id in levels(dat$human_id)) {
  tdat <- subset(dat,human_id == id)
  ctrl <- DEoptim.control(NP = 20, itermax=50)
  Bayes_same_game[[id]] <- DEoptim(Bayes_model_LL, lower=c(0), upper = c(1), data = tdat,
                                   distinct_opponent = FALSE, generalize = "game",control=ctrl)
  Bayes_same_stage[[id]] <- DEoptim(Bayes_model_LL, lower=c(0), upper = c(1), data = tdat,
                                   distinct_opponent = FALSE, generalize = "stage",control=ctrl)
  Bayes_same_no[[id]] <- DEoptim(Bayes_model_LL, lower=c(0), upper = c(1), data = tdat,
                                   distinct_opponent = FALSE, generalize = "no",control=ctrl)
  Bayes_distinct_game[[id]] <- DEoptim(Bayes_model_LL, lower=c(0), upper = c(1), data = tdat,
                                   distinct_opponent = TRUE, generalize = "game",control=ctrl)
  Bayes_distinct_stage[[id]] <- DEoptim(Bayes_model_LL, lower=c(0), upper = c(1), data = tdat,
                                        distinct_opponent = TRUE, generalize = "stage",control=ctrl)
  Bayes_distinct_no[[id]] <- DEoptim(Bayes_model_LL, lower=c(0), upper = c(1), data = tdat,
                                 distinct_opponent = TRUE, generalize = "no",control=ctrl)
}

@@

# for(id in levels(dat$human_id)) {
#   tdat <- subset(dat,human_id == id)
#   # ctrl <- DEoptim.control(NP = 20, itermax=50)
#   
#   Bayes_same_game[[id]] <- optim(c(0.1),fn=Bayes_model_LL,data=tdat, distinct_opponent = FALSE, 
#                                  generalize = "game", lower = c(0), upper = c(1),method="L-BFGS-B")
#   
#   
#   Bayes_same_stage[[id]] <- optim(c(0.1),fn=Bayes_model_LL,data=tdat, distinct_opponent = FALSE, 
#                                  generalize = "stage", lower = c(0), upper = c(1),method="L-BFGS-B")
# 
#   Bayes_same_no[[id]] <- optim(c(0.1),fn=Bayes_model_LL,data=tdat, distinct_opponent = FALSE, 
#                                  generalize = "no", lower = c(0), upper = c(1),method="L-BFGS-B")
# 
#   Bayes_distinct_game[[id]] <- optim(c(0.1),fn=Bayes_model_LL,data=tdat, distinct_opponent = TRUE, 
#                                  generalize = "game", lower = c(0), upper = c(1),method="L-BFGS-B")
# 
#   Bayes_distinct_stage[[id]] <- optim(c(0.1),fn=Bayes_model_LL,data=tdat, distinct_opponent = TRUE, 
#                                  generalize = "stage", lower = c(0), upper = c(1),method="L-BFGS-B")
# 
#   Bayes_distinct_no[[id]] <- optim(c(0.1),fn=Bayes_model_LL,data=tdat, distinct_opponent = TRUE, 
#                                  generalize = "no", lower = c(0), upper = c(1),method="L-BFGS-B")
# }
```

### 2020-08-12 Experiment_2/Experiment_2_modelling.Rmd
added BIC weights and new Bayes model

  # dat = data subset for one participant
  # opp_strategy_vec = vector of possible opponent strtegies, model assumes humans restrict opp strategy space to vector   c("level0","level1","level2")
  # return = -2logLik 
  # or "likelihood_by_trial" vector  (for later plotting, etc)
  # btwn_transfer is a boolean. True if distribution of opponent strategies is kept across games. False otherwise.

  # theta = parameter, probability computer will play its best response to what it thinks human is. Truth = 90%. in [0,1].
  # eps: parameter controlling noise in human choice. Probability human will DEVIATE from its best response. In [0,1].
  theta <- par[1]
  # eps <- par[2]

@@

  # Load tables predicting oppponent movel

@@

        # we are round 1 of stage 2, keep opp vector from round 20 of stage 1  for stage 3
        } else if (data[t,"stage"] == 2) {
            if (within_transfer){
              # hold the probs vector of Opp type learned in stage 1 in memory and save to temp.
              opp1_prior_temp <- opp_prior_vec
            if (btwn_transfer){
              # If  between games transfer get prior from opp2 prior saved from last stage of last game 
              opp_prior_vec <- opp2_prior_vec
            } else { # if no between transfer start of first interaction with secnd opp should be reset
              opp_prior_vec <- rep(1/num_strat, num_strat)
            }

@@

@@

        # Given opponent action predicted, what would be human action best response for each opp strat
        br_hum[[k]] <- exp2_best_response(t_game,as.character(pred_opp))

        # First we deal with easy case of unique predicted action ( multiple possible preds in shoot are separated by "/" sign)
        if (!grepl("/",pred_opp,fixed = TRUE)) {
           # Multiply prior by likelihood of observation to get posterior. Done here ot take advantage of For loop. 
          if(as.character(data[t,"a_action"]) == pred_opp) {
            lik_opp[k,t] <- (theta + (1-theta)/nopts)*opp_prior_vec[k]
          } else {
            lik_opp[k,t] <- ((1-theta)/nopts)*opp_prior_vec[k]
          }
        # Here we are in shootout and opponent predicted action is a vector of two possible moves (e.g "left/center")  
        } else {
          if(grepl(as.character(data[t,"a_action"]), pred_opp,fixed = TRUE)) {
            # Assume each action has likelihood of 50%
             lik_opp[k,t] <- 0.5*(theta + (1-theta)/nopts)*opp_prior_vec[k]
          } else {
            #the 2 is to standardise the theta dependent probs: P(ai plays pred | opp is level k)
            lik_opp[k,t] <- 2*((1-theta)/nopts)*opp_prior_vec[k]
          }
        }

      # Get which opponent strategy human current actn maps to (i.e, if index = 0 then human current action is best response to level-0 comp_strat...)
      indices <- which(grepl(as.character(data[t,"h_action"]),br_hum,fixed = TRUE))

      # THEN likelihood of current human action is just prior on opponent vec (haven't updated priors with curr opp act yet)
      # if action is not predicted by any level-k OM, assume human chooses randomly with prob eps
      if(length(indices) == 0){
        #lik_hum[t] <- eps/nopts
        lik_hum[t] <- 1/nopts
      # if same br action for multiple possible ai opponents, add probabilities 
      } else {
        #lik_hum[t] <- sum(opp_prior_vec[indices])*(1-eps) + eps/nopts
        lik_hum[t] <- sum(opp_prior_vec[indices])/length(indices)
      }
    }  
      # Standardising the probabilities and updating prior
      lik_opp[,t] <- lik_opp[,t]/sum(lik_opp[,t])
      opp_prior_vec <- lik_opp[,t]
    }
  # for debugging uncomment the line below
  #cat(as.character(pred_opp),as.character(data[t,"a_action"]),lik_opp[,t],"/n")
  }

@@

TOM_model(c(0.00001),test_data,c("level0","level1","level2"),"-2loglik", within_transfer = TRUE, btwn_transfer = TRUE, Naive = FALSE)
```
## Fitting Bayesian model with between game transfer (as well as within)  
```{r, cache=TRUE}
exp2_BT <- list()
for(id in unique(dat_exp2$human_id)) {
  exp2_BT[[id]] <- list()
  tdat <- subset(dat_exp2,human_id == id)

@@

## Putting all results together 
```{r}

exp2_results <- data.frame()
for(id in unique(dat_exp2$human_id)) {
exp2_results <- rbind(exp2_results,
                       data.frame(
                         "ID" = id,
                         "condition" = dat_exp2[dat_exp2$human_id==id,"condition"][1],
                         "Random_BIC" = -2*(180*log(1/3)),

                         # Bayesian updating with/without transfer
                         "Btwn_TR_BIC" = exp2_BT[[id]]$value + 2*log(180),
                         "No_Btwn_Tr_BIC" = exp2_NO_BT[[id]]$value+ 2*log(180),
                         "No_Tr_BIC" = exp2_NO_Tr[[id]]$value+ 2*log(180),
                         "Naive_BIC" = exp2_Naive[[id]]$value+ 2*log(180),

@@

```{r}
exp2_table_results <- table(exp2_results[, "condition"],c("random","TOM_BT","TOM_NBT", "TOM_NT","ToM_Naive", "QL_states","QLS_within","S_EWA","MBM")[apply(exp2_results[,c("Random_BIC","Btwn_TR_BIC","No_Btwn_Tr_BIC","No_Tr_BIC","Naive_BIC","QL_states_BIC","QLS_within_Tr_BIC","EWA_self_BIC","MBM2_BIC")],1,which.min)])

@@

```{r}
exp2_model_comp <- data.frame()
for(id in unique(dat_exp2$human_id)) {
  tdat <- subset(dat_exp2,human_id == id)
  tot_score <- sum(tdat$score)
  tot_time <- sum(tdat$human_rt)
  early_dat <- subset(tdat,between(tdat$round,2,6) & (game =="fwg"))
  #early_dat <- subset(tdat,between(tdat$round,2,6) & (game =="fwg" | game =="numbers") )
  tr_score <- sum(early_dat$score)
  id_results <- subset(exp2_results, ID == id)
  min_BIC <- apply(id_results[,c("Random_BIC","Btwn_TR_BIC","No_Btwn_Tr_BIC","No_Tr_BIC","Naive_BIC", "QL_states_BIC","QLS_within_Tr_BIC","EWA_self_BIC","MBM2_BIC")],1,min)

  best_model <- c("random","ToM_BT","ToM_NBT", "ToM_NT","ToM_Naive","QL_states","QLS_within","S_EWA", "MBM")[apply(id_results[,c("Random_BIC","Btwn_TR_BIC","No_Btwn_Tr_BIC","No_Tr_BIC","Naive_BIC","QL_states_BIC","QLS_within_Tr_BIC","EWA_self_BIC","MBM2_BIC")],1,which.min)]
  # 
  exp2_model_comp <- rbind(exp2_model_comp ,
                       data.frame(
                         "human_id" = id,
                         "condition" = dat_exp2[dat_exp2$human_id==id,"condition"][1],
                         "Early_game_score" = tr_score,
                         "Total_score" = tot_score,
                         "Best_model_2" = best_model,
                         "Total_time" = sum(tdat$human_rt),
                         "BT_minus_NBT_BIC" = id_results[,"Btwn_TR_BIC"] - id_results[,"No_Btwn_Tr_BIC"],
                         "Rand_minus_best_BIC" =  id_results[,"Random_BIC"] - min_BIC

@@

exp2_model_comp$model <- recode(exp2_model_comp$Best_model,"ToM_BT" = "btwn Tranfer","ToM_NBT" = "No btwn Transfer", "ToM_NT" = "No within or btwn Tr","QL_states" = "Q_Learning",  .default = "Random")
model <- factor(exp2_model_comp$model)
condition <- factor(exp2_model_comp$condition)

>>>>

  # dat = data subset for one participant
  # opp_strategy_vec = vector of possible opponent strategies, model assumes humans restrict opp strategy space to vector   c("level0","level1","level2")
  # return = -2logLik 
  # or "likelihood_by_trial" vector  (for later plotting, etc)
  # btwn_transfer is a boolean. True if distribution of opponent strategies is kept across games. False otherwise.

  # theta = parameter, probability computer will play its best response to what it thinks human is. Truth = 90%. in [0,1].
  theta <- par[1]

@@

  # Load tables predicting oppponent model

@@

        # we are round 1 of stage 2, keep opp vector from round 20 of stage 1  for stage 3
        } else if (data[t,"stage"] == 2) {
            if (within_transfer){
              # hold the probs vector of opponent type learned in stage 1 in memory and save to temp.
              opp1_prior_temp <- opp_prior_vec

              if (btwn_transfer){
              # If  between games transfer get prior from opp2 prior saved from last stage of last game 
                opp_prior_vec <- opp2_prior_vec
              } else { # if no between transfer start of first interaction with secnd opp should be reset
              opp_prior_vec <- rep(1/num_strat, num_strat)
              }

@@

      lik_opp[,t] <- opp_prior_vec

@@

        # Given opponent action predicted, what would be human action best response for each opp strat
        br_hum[[k]] <- as.character(exp2_best_response(t_game,as.character(pred_opp)))

        # First we deal with easy case of unique predicted action ( multiple preds in shoot are separated by "/" sign)
        if (!grepl("/",pred_opp,fixed = TRUE)) {
           # Multiply prior by likelihood of observation to get posterior. Done here ot take advantage of For loop. 
          if(as.character(data[t,"a_action"]) == pred_opp) {
            lik_opp[k,t] <- (theta + (1-theta)/nopts)*opp_prior_vec[k]
          } else {
            lik_opp[k,t] <- ((1-theta)/nopts)*opp_prior_vec[k]
          }
        # Here we are in shootout and opponent predicted action is a vector of two possible moves (e.g "left/center")  
        } else {
          if(grepl(as.character(data[t,"a_action"]), pred_opp,fixed = TRUE)) {
            # Assume each action has likelihood of 50% 
             lik_opp[k,t] <- (0.5*(theta + (1-theta)/nopts) + 0.5*((1-theta)/nopts)) *opp_prior_vec[k]
          } else { 
            lik_opp[k,t] <- ((1-theta)/nopts)*opp_prior_vec[k]
          }
        }
      }  
      # Get which opponent strategy human current actn maps to (i.e, if index = 0 then human current action is best response to level-0 comp_strat...)
      indices <- which(grepl(as.character(data[t,"h_action"]),br_hum,fixed = TRUE))
      not_pred_indx <- setdiff(c(1,2,3),indices)
      # cat(as.character(indices), "\n")

      # THEN likelihood of current human action is just sumproduct of priors and likelihood of each oppoennt action
      if (!grepl("/",br_hum,fixed = TRUE)) {
        lik_hum[t] <- sum(opp_prior_vec[indices])* (theta + (1-theta)/nopts) +    sum(opp_prior_vec[not_pred_indx])*(1-theta)/nopts
      } else {
        for (i in 1:3) {
          temp <- 0
          if (grepl("/",br_hum[i],fixed = TRUE)) {
            temp <- temp + 0.5*(theta + (1-theta)/nopts)*opp_prior_vec[i]
          } else{
            temp <- temp + 
          }
        }
        lik_hum[t] <- sum(opp_prior_vec[indices])* (theta + (1-theta)/nopts) +    sum(opp_prior_vec[not_pred_indx])*(1-theta)/nopts
      }

      # Standardising the probabilities and updating prior
      lik_opp[,t] <- lik_opp[,t]/sum(lik_opp[,t])
      opp_prior_vec <- lik_opp[,t]
    } # End of else ( from round 2 onwards)

  # for debugging uncomment the line below
  # cat(as.character(data[t,"a_action"]),lik_opp[,t],"\n")
  cat(as.character(br_hum),as.character(data[t,"h_action"]),lik_hum[t],"\n","\n")

@@

TOM_model(c(0.5),test_data,c("level0","level1","level2"),"-2loglik", within_transfer = TRUE, btwn_transfer = TRUE, Naive = FALSE)

```
## Fitting Bayesian model with between game transfer (as well as within)  
```{r, cache=TRUE}
exp2_BT <- list()
for(id in unique(dat_exp2$human_id)) {
  exp2_BT[[id]] <- list()
  tdat <- subset(dat_exp2,human_id == id)

@@

## Putting all results together 
```{r}
exp2_results <- data.frame()
for(id in unique(dat_exp2$human_id)) {
exp2_results <- rbind(exp2_results,
                       data.frame(
                         "ID" = id,
                         "condition" = dat_exp2[dat_exp2$human_id==id,"condition"][1],
                         "Random_BIC" = -2*(180*log(1/3)),
# 
# #                          # Bayesian updating with/without transfer
#                          "Btwn_TR_BIC" = exp2_BT[[id]]$value + 2*log(180),
#                          "No_Btwn_Tr_BIC" = exp2_NO_BT[[id]]$value+ 2*log(180),
#                          "No_Tr_BIC" = exp2_NO_Tr[[id]]$value+ 2*log(180),
#                          "Naive_BIC" = exp2_Naive[[id]]$value+ 2*log(180),

                         # MS results for Bayesian models
                         #  # Bayesian updating with between and within game transfer
                         "Distinct_game_BIC" = Bayes_distinct_game[[id]]$value + 2*log(180),
                          # Bayesian updating with within but no btwn game transfer
                         "Distinct_stage_BIC" = Bayes_distinct_stage[[id]]$value + 2*log(180),
                          #  No within or between game transfer
                         "Bayes_distinct_no" = Bayes_distinct_no[[id]]$value + 2*log(180),
                          # No distinction between players, transfer within and between
                         "Bayes_same_game" = Bayes_same_game[[id]]$value + 2*log(180),

@@

```{r}
# WIth IG results for Bayesian models
# exp2_table_results <- table(exp2_results[, "condition"],c("random","TOM_BT","TOM_NBT", "TOM_NT","ToM_Naive", "QL_states","QLS_within","S_EWA","MBM")[apply(exp2_results[,c("Random_BIC","Btwn_TR_BIC","No_Btwn_Tr_BIC","No_Tr_BIC","Naive_BIC","QL_states_BIC","QLS_within_Tr_BIC","EWA_self_BIC","MBM2_BIC")],1,which.min)])

# WIth MS results for Bayesian models
exp2_table_results <- table(exp2_results[, "condition"],c("random","TOM_BT","TOM_NBT", "TOM_NT","ToM_Naive", "QL_states","QLS_within","S_EWA","MBM")[apply(exp2_results[,c("Random_BIC","Distinct_game_BIC","Distinct_stage_BIC","Bayes_distinct_no","Bayes_same_game","QL_states_BIC","QLS_within_Tr_BIC","EWA_self_BIC","MBM2_BIC")],1,which.min)])

@@

```{r}
# WITH MS results for bayesian models 
# exp2_table_results <- table(exp2_results[, "condition"],c("random","TOM_BT","TOM_NBT", "TOM_NT","ToM_Naive", "QL_states","QLS_within","S_EWA","MBM")[apply(exp2_results[,c("Random_BIC","Distinct_game_BIC","Distinct_stage_BIC","Bayes_distinct_no","Bayes_same_game","QL_states_BIC","QLS_within_Tr_BIC","EWA_self_BIC","MBM2_BIC")],1,which.min)])
# 
#  write.csv(exp2_table_results,file="exp2_table_results.csv",row.names = TRUE)
#  kable(exp2_table_results)
```

```{r}
exp2_model_comp <- data.frame()
for(id in unique(dat_exp2$human_id)) {
  tdat <- subset(dat_exp2,human_id == id)
  tot_score <- sum(tdat$score)
  tot_time <- sum(tdat$human_rt)
  early_dat <- subset(tdat,between(tdat$round,2,6) & (game =="fwg"))
  #early_dat <- subset(tdat,between(tdat$round,2,6) & (game =="fwg" | game =="numbers") )
  tr_score <- sum(early_dat$score)
  id_results <- subset(exp2_results, ID == id)

  # IG BAYES MODELS 
  # min_BIC <- apply(id_results[,c("Random_BIC","Btwn_TR_BIC","No_Btwn_Tr_BIC","No_Tr_BIC","Naive_BIC", "QL_states_BIC","QLS_within_Tr_BIC","EWA_self_BIC","MBM2_BIC")],1,min)
  # 
  # best_model <- c("random","ToM_BT","ToM_NBT", "ToM_NT","ToM_Naive","QL_states","QLS_within","S_EWA", "MBM")[apply(id_results[,c("Random_BIC","Btwn_TR_BIC","No_Btwn_Tr_BIC","No_Tr_BIC","Naive_BIC","QL_states_BIC","QLS_within_Tr_BIC","EWA_self_BIC","MBM2_BIC")],1,which.min)]

  # MS BAYES MODELS
  min_BIC <- apply(id_results[,c("Random_BIC","Distinct_game_BIC","Distinct_stage_BIC","Bayes_distinct_no","Bayes_same_game", "QL_states_BIC","QLS_within_Tr_BIC","EWA_self_BIC","MBM2_BIC")],1,min)

  best_model <- c("random","ToM_BT","ToM_NBT", "ToM_NT","ToM_Naive","QL_states","QLS_within","S_EWA", "MBM")[apply(id_results[,c("Random_BIC","Distinct_game_BIC","Distinct_stage_BIC","Bayes_distinct_no","Bayes_same_game","QL_states_BIC","QLS_within_Tr_BIC","EWA_self_BIC","MBM2_BIC")],1,which.min)]

  # 
  exp2_model_comp <- rbind(exp2_model_comp ,
                       data.frame(
                         "human_id" = id,
                         "condition" = dat_exp2[dat_exp2$human_id==id,"condition"][1],
                         "Early_game_score" = tr_score,
                         "Total_score" = tot_score,
                         "Best_model_2" = best_model,
                         "Total_time" = sum(tdat$human_rt),
                         # "BT_minus_NBT_BIC" = id_results[,"Btwn_TR_BIC"] - id_results[,"No_Btwn_Tr_BIC"],
                         "BT_minus_NBT_BIC" = id_results[,"Distinct_game_BIC"] - id_results[,"Distinct_stage_BIC"],
                         "Rand_minus_best_BIC" =  id_results[,"Random_BIC"] - min_BIC

@@

# exp2_model_comp$model <- recode(exp2_model_comp$Best_model,"ToM_BT" = "btwn Tranfer","ToM_NBT" = "No btwn Transfer", "ToM_NT" = "No within or btwn Tr","QL_states" = "Q_Learning",  .default = "Random")

exp2_model_comp$model <- recode(exp2_model_comp$Best_model,"ToM_BT" = "btwn Tranfer","ToM_NBT" = "No btwn Transfer", "ToM_NT" = "No within or btwn Tr","QL_states" = "Q_Learning",  .default = "Random")

model <- factor(exp2_model_comp$model)
condition <- factor(exp2_model_comp$condition)
